Quantitative Auditing of Fairness Measures with Differentially Private Synthetic Data

### 2024-12-01 paper/paper.tex
subtable will overflow
some progress

\begin{table}[h]
\caption{Example marginals.}
\label{tab:marginal-example}
\centering
\begin{subtable}[t]{0.45\linewidth}
\centering
\caption{Marginal of original data.}
\begin{tabular}{cc}
\toprule
Attributes & Count \\
\midrule
Male,White & 24 \\
Female,White & 33 \\
Male,Black & 13 \\
Female,Black & 47 \\
\bottomrule
\end{tabular}
\end{subtable}
\hspace{0.05\linewidth}
\begin{subtable}[t]{0.45\linewidth}
\centering
\caption{Marginal of synthetic data.}
\begin{tabular}{cc}
\toprule
Attributes & Count \\
\midrule
Male,White & 22 \\
Female,White & 35 \\
Male,Black & 10 \\
Female,Black & 46 \\
\bottomrule
\end{tabular}
\end{subtable}
\end{table}

@@

@@

\begin{table}[h]
\caption{Fairness measures experiment results of the COMPAS dataset. Average of differences is 0.031.}
\label{tab:diabetes_score}
\begin{tabular}{cccc}
\toprule
\textbf{Measure} & \textbf{Original} & \textbf{Synthetic} & \textbf{Difference} \\
\midrule
Demographic Parity  & 0.013 & 0.015 & 0.002 \\
Accuracy Eqaulity   & 0.007 & 0.009 & 0.002 \\
Equalized Odds 1    & 0.000 & 0.003 & 0.003 \\
Equalized Odds 2    & 0.008 & 0.106 & 0.097 \\
Accuracy Equality 1 & 0.013 & 0.097 & 0.084 \\
Accuracy Equality 2 & 0.021 & 0.020 & 0.001 \\
\bottomrule
\end{tabular}
\end{table}

@@

@@

>>>>

\begin{table}[h]
\caption{Example marginals.}
\label{tab:marginal-example}
\centering
\begin{subtable}[t]{0.45\linewidth}
\centering
\caption{Marginal of original data.}
\begin{tabular}{cc}
\toprule
Attributes & Count \\
\midrule
Male,White & 24 \\
Female,White & 33 \\
Male,Black & 13 \\
Female,Black & 47 \\
\bottomrule
\end{tabular}
\end{subtable}
\begin{subtable}[t]{0.45\linewidth}
\centering
\caption{Marginal of synthetic data.}
\begin{tabular}{cc}
\toprule
Attributes & Count \\
\midrule
Male,White & 22 \\
Female,White & 35 \\
Male,Black & 10 \\
Female,Black & 46 \\
\bottomrule
\end{tabular}
\end{subtable}
\end{table}

@@

% \begin{table}[h]
% \caption{Example marginals.}
% \label{tab:marginal-example}
% \centering
% \begin{subtable}[t]{0.3\linewidth}
%   \caption{Fairness measures experiment results of the adult dataset. Average of differences is 0.0431.}
%   \label{tab:adult_score}
%   \begin{tabular}{ccccc}
%   \toprule
%   \textbf{Measure} & \textbf{Original} & \textbf{Synthetic} & \textbf{Difference} \\
%   \midrule
%   Demographic Parity  & 0.172 & 0.104 & 0.067 \\
%   Accuracy Eqaulity   & 0.047 & 0.117 & 0.069 \\
%   Equalized Odds 1    & 0.057 & 0.079 & 0.021 \\
%   Equalized Odds 2    & 0.166 & 0.122 & 0.044 \\
%   Accuracy Equality 1 & 0.100 & 0.132 & 0.031 \\
%   Accuracy Equality 2 & 0.119 & 0.146 & 0.027 \\
%   \bottomrule
%   \end{tabular}
% \end{subtable}
% \begin{subtable}[t]{0.3\linewidth}
%   \centering
%   \caption{Fairness measures experiment results of the COMPAS dataset. Average of differences is 0.031.}
%   \label{tab:diabetes_score}
%   \begin{tabular}{cccc}
%   \toprule
%   \textbf{Measure} & \textbf{Original} & \textbf{Synthetic} & \textbf{Difference} \\
%   \midrule
%   Demographic Parity  & 0.013 & 0.015 & 0.002 \\
%   Accuracy Eqaulity   & 0.007 & 0.009 & 0.002 \\
%   Equalized Odds 1    & 0.000 & 0.003 & 0.003 \\
%   Equalized Odds 2    & 0.008 & 0.106 & 0.097 \\
%   Accuracy Equality 1 & 0.013 & 0.097 & 0.084 \\
%   Accuracy Equality 2 & 0.021 & 0.020 & 0.001 \\
%   \bottomrule
%   \end{tabular}
% \end{subtable}
% \end{table}

@@

\begin{table}[h]
\caption{Fairness measures experiment results of the diabetes dataset. Average of differences is 0.031.}
\label{tab:diabetes_score}
\begin{tabular}{cccc}
\toprule
\textbf{Measure} & \textbf{Original} & \textbf{Synthetic} & \textbf{Difference} \\
\midrule
Demographic Parity  & 0.013 & 0.015 & 0.002 \\
Accuracy Eqaulity   & 0.007 & 0.009 & 0.002 \\
Equalized Odds 1    & 0.000 & 0.003 & 0.003 \\
Equalized Odds 2    & 0.008 & 0.106 & 0.097 \\
Accuracy Equality 1 & 0.013 & 0.097 & 0.084 \\
Accuracy Equality 2 & 0.021 & 0.020 & 0.001 \\
\bottomrule
\end{tabular}
\end{table}

@@

Our experiments showed that synthetic data generally preserves the fairness properties with a reasonable degree of accuracy. The average of the differences between the fairness measure values of the original and synthetic datasets is below 0.1 for all datasets. This indicates that synthetic data is a good approximation of the original data in terms of fairness.

In particular, for the adult dataset, the average difference was 0.0431, suggesting a close match between the synthetic and the original data in terms of fairness measures. For the diabetes dataset, the average difference was 0.031, which is even lower. Even in the case of the COMPAS dataset, which had a higher value, it was still within an acceptable range at 0.069.

This demonstrated that synthetic data can accurately reflect the fairness properties of the original data. Therefore, fairness analyses performed on synthetic data will yield results consistent with those on the original data.

@@

Let the standalone symbols denote the case of being equal to one and the overlined symbols denote the case of being equal to zero. For example, $S$ denotes the case of $S = 1$ and $\overline{S}$ denotes the case of $S = 0$.

independence
\[
P[\hat{Y} | S] - P[\hat{Y} | \overline{S}]
= \frac{P[\hat{Y} \cap S]}{P[\overline{S}]} - \frac{P[\hat{Y} \cap \overline{S}]}{P[\overline{S}]}
\]

separation
\[
P[\hat{Y} | S, Y] - P[\hat{Y} | \overline{S}, Y]
= \frac{P[\hat{Y} \cap S \cap Y]}{P[\overline{S} \cap Y]} - \frac{P[\hat{Y} \cap \overline{S} \cap Y]}{P[\overline{S} \cap Y]}
\]

sufficiency
\[
P[Y | S, \hat{Y}] - P[Y | \overline{S}, \hat{Y}]
= \frac{P[Y \cap S \cap \hat{Y}]}{P[\overline{S} \cap \hat{Y}]} - \frac{P[Y \cap \overline{S} \cap \hat{Y}]}{P[\overline{S} \cap \hat{Y}]}
\]
